\title{Fire Risk Assessment\\
    London Hackspace \\
    Units 23 \& 24\\
    Cremer Business Centre\\
    London E2 8HD
}


\date{3\rd October 2012}

\author{Russell Garrett}

\maketitle

\subsection{Introduction}

The London Hackspace is a community-run non-profit workspace run with
the object of fostering cross-disciplinary technical, scientific, and
artistic skills through social collaboration and education.

The space includes desk space and classrooms as well as facilities for
cooking, electronics, textiles, woodworking, metalworking, and amateur
science.

London Hackspace is funded almost entirely by membership subscriptions
from its members.

Overall responsibility for safety in the Hackspace is held by the
member-elected Board of Trustees of London Hackspace Ltd. The facilities
are run by volunteer members, with the Trustees only stepping in if
problems are encountered. London Hackspace has no employees.

\subsection{Building}

London Hackspace is located in two light industrial units on the second
floor of the Cremer Business Centre, with a total floor area of 2600 sq
ft. The fire alarm system is provided by the landlord.

The construction of the building is brick and concrete, and all internal
walls are plasterboard on wood studding.

\subsection{Sources of Ignition}

\subsubsection{Electrical}

All circuits at London Hackspace are protected by MCBs.

Ring circuits in unit 23 and the kitchen in unit 24 are also protected
by residual current devices.

Cooking applicances in the kitchen are all electric, so ignition risk is
low.

\subsubsection{Workshop}

The workshop contains several tools which constitute a risk of ignition:

\begin{itemize}
\item
  The laser cutter constitutes a high risk of ignition when used on
  certain materials. Users of the laser cutter are required to be
  trained, and are required to watch the machine during cutting. A \COtwo
  fire extinguisher is provided for extinguishing fires in the laser
  cutter, which is not considered part of the standard fire protection.
\item
  The welding and grinding tools produce a lot of sparks which represent
  a risk of ignition. Users of these tools are made aware of the risks
  and the location of firefighting equipment.
\end{itemize}
\subsubsection{Other}

Smokers use the external balconies. Containers are provided for
cigarette butts.

\subsection{Sources of Fuel}

The fabric of the building is concrete. Sources of fuel in Unit 24 are
primarily upholstery.

The workshop is used for woodworking and fuel exists there in the form
of wood and sawdust. As a volunteer-run workshop, housekeeping is a
problem. We are working on improving this, and the cleanliness of the
workshop is currently checked weekly.

\subsection{People at Risk}

The London Hackspace is used by its members and their guests. There are
usually between 5 and 25 people in the space.

\subsection{Escape Routes}

The front door of unit 23 (the workshop area) is intentionally blocked,
however there are still two independent fire exits, so this remains in
compliance with current building regulations.

The rear fire exits of both units lead to separate fire escapes. Escape
routes are not currently signed.

Emergency lighting is currently not provided, however both units have
windows which allow emergency lighting to enter from the balconies.

\subsection{Protection Measures}

One 2kg \COtwo extinguisher is located by the emergency exits in both Unit
23 and Unit 24. A 7kg dry powder extinguisher is located at the doorway
between both units. The seals on these are checked monthly.

A 2kg \COtwo extinguisher is located by the laser cutter, however this is
not considered as a protection measure as it is frequently used to
handle low-level fires.

\subsection{Findings}

\subsubsection{3\rd October 2012}
\begin{enumerate}
\item
  Pushbars should be fitted on rear fire exit doors, and locks removed
  (already rectified)
\item
  Fire exits and extinguishers should be signed.
\item
  Consider the cost of installing emergency lighting.
\item
  Ensure regular checks of housekeeping, fire extinguishers, and fire
  exits.
\end{enumerate}
