\title{London Hackspace\\
    1st July Open Day\\
    Event Management Plan
}


\date{13th October 2013}

\author{Russell Garrett}

\maketitle

\section{About London Hackspace}

The London Hackspace is a non-profit members-run community workshop in London.
Funded by membership subscriptions and donations, we aim to provide a space for
our members to use tools and equipment they might not be able to access at
home, as well as socialise with other like-minded members of the community.

Tools available include laser cutters, 3D printers, electronics equipment,
as well as more traditional woodworking, metalworking, and fabrics facilties.

Since being founded in 2009, London Hackspace has expanded to over 750 members
and, as of April 2013, now occupies a 6500 sq ft premises on Hackney Road.
The space consists of a ground floor area for clean working, including a
classroom and a social area, as well as a basement workshop.

\section{About the Open Day}

Periodically London Hackspace holds open days to display the space to the public,
to encourage potential members to join, and to raise funds. We've succesfully
run seven of these events before (three at the current premises) with very positive
results.

These events are publicised in the wider community and any members of the public are
invited to attend. The event is run during the afternoon and we plan to close to
the public by approximately 23:00. After this, the space will be accessible only
to members and their guests.

\section{Capacity}

The event will be held primarily in our ground floor area (capacity ~150) and yard
(capacity ~200) with tours being run around our basement workshops (capacity ~50).

The most recent of our open days had an estimated attendance of 200. Most visitors
don't stay longer than half an hour, and the peak capacity is around 80. We do not
anticipate seeing more than double these numbers at this event.

\section{Staff}

There will be at least ten volunteer London Hackspace members on the premises while
they are open to the public. Telephone numbers will be shared with the designated
event manager in case of emergency.

One member of staff will be stationed on the door.

\section{Drinks}

A TEN for alcohol has been applied for. We intend to sell alcohol - primarily in the
form of beer - as well as soft drinks at retail prices to raise money. Those selling
beer will be briefed in the licensing rules. Drinking water will be provided for free.

\section{Noise}

A license for regulated entertainment has not been applied for, and no music will be
played during the event. We are keen to maintain good relationships with our neighbours,
and any organised events in the yard will finish by 22:00.

\section{Toilets}

There are three unisex toilets on the premises, one of which is disabled-friendly.
This is more than the amount recommended by the HSE Event Safety Guide for
our licensed capacity, and much larger than that recommended for our expected peak.

\section{First Aid}

London Hackspace has extensive up-to-date first aid equipment and a qualified first aider will be on site.

\section{Event Contact}

Russ Garrett (Event Manager \& Licensee)

2 Ockendon Mews \\
London N1 3JL

Email: russ@london.hackspace.org.uk \\
Telephone:  (email contact preferred, unless urgent)


\begin{landscape}

\section{General Risk Assessment}

\begin{tabular}{ | p{3cm} | l | p{1.5cm} | p{8cm} | p{1.5cm} | p{2cm} | p{5cm} | }
\hline
\textbf{Hazard} & \textbf{Risk} & \textbf{Affected Parties}
& \textbf{Control Measures} & \textbf{Resulting Risk} \\ \hline

Electrocution & Low & Everyone &
Electrical installation is new and has been recently checked. Regular visual checks occur. &
Low \\ \hline

Trips \& Falls & Medium & Everyone &
Premises to be checked for trip hazards before event start. Steep stairs exist down to the workshop,
treads are clearly marked. & Medium \\ \hline

Injury from tools or chemicals & Medium & Everyone &
Area which public can access unsupervised will be cleared of dangerous items. Public to be supervised
in tours around workshops.
& Low  \\ \hline

Public order issues & Low & Everyone &
Most public are not expected to stay long; no previous problems have been reported; bar staff will be briefed.
& Low  \\ \hline

Fire & \multicolumn{4}{|c|}{See attached Fire Risk Assessment} \\ \hline

\end{tabular}
\end{landscape}

